2H qSIP Calculations

### 2021-10-19 qSIP_calculations.Rmd
add zero time points, resolve ambiguous peaks

@@

@@

```{r}
# Generate an isoverse peak map
peaks_mapped <- peak_table %>%
  iso_map_peaks(peak_map, map_id = Analysis) %>%
  filter(!is.na(compound))
```

# Generation Time Calculations

@@

@@

mtda <- read_csv(file.path("data", "sample_metadata_2021.csv"))
sample_names <- mtda$id1

peaks_mapped <- peaks_mapped %>% 
  filter(sample_id %in% sample_names)

@@

inc_time_zero <- peaks_mapped %>% 
  filter(inc_time_d == 0) %>% 
  select(sample_id, compound, at2H) %>% 
  mutate(f_start = at2H)
         # extract first and lass code of sample_id

@@

>>>>

# Turnover Calculation Function

@@

## Load Metadata and Problematic Run Data

```{r}
mtda <- read_csv(file.path("data", "sample_metadata_2021.csv"))
sample_names <- mtda$id1

problematic_runs <- read_xlsx(file.path("data", "IRMS", "problematic_runs.xlsx"))
```

@@

## Generate Isoverse Peak Map
```{r}
# Generate an isoverse peak map
peaks_mapped <- peak_table %>%
  iso_map_peaks(peak_map, map_id = Analysis) %>%
  filter(!is.na(compound))

@@

## Remove readychecks, blanks, etc. from analysis
```{r}
# Filter based on what is in the sample_names metadata
peaks_mapped <- peaks_mapped %>% 
  filter(sample_id %in% sample_names)

# Filter out runs that are on our problematic_runs list
peaks_mapped <- peaks_mapped %>% 
  filter(Analysis %nin% problematic_runs)
```

## Check problematic peak assignments
```{r}
problem_peaks <- iso_get_problematic_peak_mappings(peaks_mapped)
```

@@

@@

inc_time_zero <- peaks_mapped %>% 
  filter(inc_time_d == 0) %>% 
  select(sample_id, compound, at2H, t_series_id) %>% 
  mutate(f_start = at2H) %>% 
  select(-at2H)

## Trying a simpler example
c_inc_time_zero <- inc_time_zero %>% 
  filter(str_detect(t_series_id, "c"))

c_peaks_mapped <- peaks_mapped %>% 
  filter(str_detect(t_series_id, "c")) %>% 
  full_join(c_inc_time_zero, by = c("t_series_id", "compound"))

@@

```{r}
zero_peaks <- peaks_mapped %>%
  filter(inc_time_d_str == "0 Days") %>%
  group_by(t_series_id, compound) %>%
  mutate(n_analyical_reps = n()) %>%
  ungroup() %>%
  # exclude ambiguous peaks and those with multiple data points
  # this needs to be fixed
  filter(!is_ambiguous, n_analyical_reps == 1)

peaks_mapped_with_zeros <- 
  peaks_mapped %>%
  left_join(
    zero_peaks %>%
      select(
        compound, t_series_id, zero_sample_id = sample_id, area2_zero = area2, d2H_zero = d2H
      ),
    by = c("t_series_id", "compound")
  ) 
stopifnot(nrow(peaks_mapped_with_zeros) == nrow(peaks_mapped))

# no zero samples
peaks_mapped_with_zeros %>% filter(is.na(zero_sample_id)) %>% View()
```

```{r}
#peak maps
peaks_mapped %>%
  ungroup() %>%
  select(Analysis, compound, rt) %>%
  mutate(rt = round(rt, digits=0)) %>%
  pivot_wider(
    names_from = Analysis, 
    names_prefix = "rt:",
    values_from = rt, 
    id_cols = compound, 
    values_fn = function(x) paste(x, collapse = "; ")
  ) %>%
  openxlsx::write.xlsx(file.path("data", "IRMS", "peak_maps_resolve.xlsx"))
```
